---
title: "Does College Strength of Schedule Really Matter?"
author: "Nick Kalinowski"
date: "9/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("scales", repos = "http://cran.us.r-project.org")
library(DT)
library(tidyverse)
library(ggplot2)
library(class)
library(caret)
library(kableExtra)
library(knitr)
```

## Overview

Among NBA draft circles, strength of schedule is often a hot-button topic when discussing potential draftees, particularly those who come from mid-major schools. In recent years, players such as Ja Morant and Grant Riller, or more recently Patrick Baldwin Jr., have emerged as legitimate pro prospects despite playing at a lower level of competition. In response, many in the draft community, including myself, have discounted some of their college accomplishments by citing the low quality of opposition these players face on a nightly basis. 

In this project, I will seek to answer the question of whether or not college strength of schedule (referred from here on out as "SOS") should really be a potential consideration for NBA scouts, or if it really is extraneous (i.e. the idea that "talent translates regardless of level"). SOS data was scraped from basketball-reference using the BeautifulSoup package in Python, DARKO metrics were downloaded from Kostya Medvedovsky's shiny site (linked at the end of this document), and LEBRON data collected from Bball Index. Data was obtained for every player drafted since 2010. 

## General Facts About the Dataset

In total, the dataset includes 532 players, all of whom played at least one game at a NCAA Division 1 University. Since data was not available for junior colleges or non-Division 1 institutions, these players were omitted. The SOS data metric collected was the one for a player's entire career, rather than a single season, to average out any differences that may exist between any multi-year college player's career, as well as factor in any other variables such as transferring schools. 


Here is a brief synopsis of some of the data scraped from basketball-reference: 

```{r }
nba_data = read.csv("NewNBADraftData.csv")

kable(nba_data[1:7], caption="Scraped Data")
```

The distribution of SOS among the prospects in the dataset can be displayed as follows:

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
